MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites \\ Supplementary Material

### 2014-12-08 chapters/MetaTracts.tex
Updated  reviews

Frangi et al.~\cite{Frangi1998} introduced a process that searches for geometric structures which are tubular. They define a measure based on two geometric ratios of the second order ellipsoid given by the local Hessian matrix to measure the ``vesselness'' criterion.  In order to determine reliable Hessians, we compute a similar metric. We include their work here for completeness and direct the reader to ~\cite{Frangi1998} for details. Let $\lambda_{K}$ be the eigenvalue with the $K^{th}$ smallest magnitude. Here, $|{\lambda}_{1}| \leq| {\lambda}_{2}|\leq| {\lambda}_{3}| $ are the eigenvalues of the Hessian matrix. Specifically, a pixel belonging to a vessel region will have small $\lambda_{1}$ ($|\lambda_{1}|\approx 0$) and $\lambda_{2}$, $\lambda_{3}$ of large magnitude and of equal sign($|\lambda_{1}| \ll |\lambda_{2}|$ and $|\lambda_{2}|\approx |\lambda_{3}|$). The sign indicates if the vessel is bright in a dark background or dark in a bright background. In our case the individual fibers are bright ($\lambda_2,\lambda_3 < 0$). The following measures are defined in~\cite{Frangi1998}.  

@@

\section{Conclusion and future work}
\label{sec:conclusions}
In this paper, we introduce a framework to extract and visualize fiber bundles in composite materials. We show that our framework works at comparatively low resolution and with dense fiber arrangements (when extracting single fibers might not be possible). It handles complex fiber patterns such as ``cross overs'' and ``braiding''. We perform an user evaluation to indicate the usefulness of the method. In future, we plan to increase the precision of the extractions, include uncertainty based visualization to better portray the surface of separations and speed up extraction times.
%
%\begin{figure}
%  \centering
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-scalar.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-1.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-a.eps}}
%    \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-b.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-labels-all.eps}}
%  \caption{Dense data set with bundles which are flat and thin. (a) shows the results original dataset, (b) shows the results of metaTract extraction, (c) shows the results of our two step clustering  into 14 classes. (d) shows the results of voxelization  and (e) shows the results of surface extraction. }\label{fig:crop-6}
%\end{figure}
%% if specified like this the section will be ommitted in review mode

>>>>

Frangi et al.~\cite{Frangi1998} introduced a process that searches for geometric structures which are tubular. They define a measure based on two geometric ratios of the second order ellipsoid given by the local Hessian matrix to measure the ``vesselness'' criterion.  In order to determine reliable Hessians, we compute 
\color{red}{ the same metric} \color{blue}{a similar metric}\color{black}. We include their work here for completeness and direct the reader to ~\cite{Frangi1998} for details. Let $\lambda_{K}$ be the eigenvalue with the $K^{th}$ smallest magnitude. Here, $|{\lambda}_{1}| \leq| {\lambda}_{2}|\leq| {\lambda}_{3}| $ are the eigenvalues of the Hessian matrix. Specifically, a pixel belonging to a vessel region will have small $\lambda_{1}$ ($|\lambda_{1}|\approx 0$) and $\lambda_{2}$, $\lambda_{3}$ of large magnitude and of equal sign($|\lambda_{1}| \ll |\lambda_{2}|$ and $|\lambda_{2}|\approx |\lambda_{3}|$). The sign indicates if the vessel is bright in a dark background or dark in a bright background. In our case the individual fibers are bright ($\lambda_2,\lambda_3 < 0$). The following measures are defined in~\cite{Frangi1998}.  

@@

\section{Limitations and future work}
\label{sec:conclusions}
\color{red}
 A key assumption of the method is ``connectivity'' (Sec.~\ref{sec:char_data}).
If the ``connectivity'' is not satisfied due to noise in the image, the then MetaTracts will be inaccurate. 
The clustering process also assumes that the fiber bundles have a minimum width.
\color{green}
In this paper, we introduce a framework to extract and visualize fiber bundles in composite materials. We show that our framework works at comparatively low resolution and with dense fiber arrangements (when extracting single fibers might not be possible). It handles complex fiber patterns such as ``cross overs'' and ``braiding''. We perform an user evaluation to indicate the usefulness of the method.
\color{black} In future, we plan to increase the precision of the extractions, include uncertainty based visualization to better portray the surface of separations and speed up extraction times.
%
%\begin{figure}
%  \centering
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-scalar.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-1.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-a.eps}}
%    \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-b.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-labels-all.eps}}
%  \caption{Dense data set with bundles which are flat and thin. (a) shows the results original dataset, (b) shows the results of metaTract extraction, (c) shows the results of our two step clustering  into 14 classes. (d) shows the results of voxelization  and (e) shows the results of surface extraction. }\label{fig:crop-6}
%\end{figure}
%% if specified like this the section will be ommitted in review mode
